---
title: 'Practical 6: Logistic regression and K means clustering'
author: "WST 212 2019"
date: "Due date: 20 May on or before 14h30"
output:
  pdf_document: default
  html_document: default
---

```{r echo=FALSE, message=FALSE}
library(readr)
library(tidyverse)
library(datasets)
library(ggplot2)
library(grid)
library(png)
library(readxl)
library(KODAMA)

```

# **Question 1**


```{r}
Grades = read_excel("Grades.xls")

Grades$LetterGrade = NULL
Grades$GRADE = ifelse(Grades$GRADE == 1, "A", "BC")

Grades$GRADE = as.factor(Grades$GRADE)
Grades$PSI = as.factor(Grades$PSI)

Grades.logistic1 = glm(GRADE ~., data = Grades, family = binomial(link = logit))
summary(Grades.logistic1)

Grades.logistic3 = glm(GRADE ~.  -TUCE, data = Grades, family = binomial(link = logit))
summary(Grades.logistic3)


```
The final model is given by
$ln(\frac{\hat{p}(y-1)}{1-\hat{p}(y-1)})=\hat{\beta}_{0}+\hat{\beta}_{1}(GPA)+\hat{\beta}_{2}(PSI)$

The best model is:

$ln(\frac{\hat{p}(y-1)}{1-\hat{p}(y-1)})=-11.602+3063(GPA)+2.338(PSI)$

Now we have that

$p=\frac{\exp(\hat{\beta}_{0}+\hat{\beta}_{1}(GPA)+\hat{\beta}_2(PSI))}{1+\exp(\hat{\beta}_{0}+\hat{beta}_{1}(GPA)+\hat{\beta}_{2}(PSI))} = \frac{odds}{1+odds}$

**c)**
1) $p=\frac{\exp(-11.602 + 3.063(3) + 2.338(1))}{1 + \exp(-11.602 + 3.063(3) + 2.338(1)} = 0.4812$


# **Question 2**
```{r}

```


Show in New WindowClear OutputExpand/Collapse Output
 Show Traceback
Error in library(readr) : there is no package called ‘readr’
# **Question 3**

```{r , message=FALSE}
img = readPNG("cluster_image.png")

# Obtain the dimension
imgDm = dim(img)

# Create the data matrix
d1 = data.frame(
  R = matrix(img[,,1], ncol=1),
  G = matrix(img[,,2], ncol=1),
  B = matrix(img[,,3], ncol=1)
)

# Cluster image
 #Fill in cluster number here
num_clust = ...   
clusts = kmeans(d1, centers = num_clust)
#get centroids
centers = clusts$centers    
#replace all clustered RGB entries with centroids
d2=centers[clusts$cluster,] 

#create a char vector of hex decimal for data from d2
img2 = rgb(d2[,1],d2[,2],d2[,3]) 
#reshape the char vector into dimensions of original image
dim(img2) = c(imgDm[1],imgDm[2]) 

grid.newpage()
grid.raster(img2)
```


# **Question 4**

```{r}

```




